Constructive Solid Geometry for Interactive Environments

### 2018-04-29 Paper.tex
Recreate die and connector OpenSCAD files
Create presentation

The increased movement of the game objects highlighted one major challenge of converting the OpenSCAD designs to OpenGL. OpenSCAD uses a right-handed coordinate system, while OpenGL uses a left-handed system.
\begin{figure}[h]
  \includegraphics[width=12cm]{Right-Hand}
  \centering
  \caption{The OpenSCAD viewer. As indicated by the legend in the bottom-left corner, the program uses a right-handed coordinate system (the positive z-axis is pointing up). In a left-handed coordinate system, such as the one used by OpenGL, the negative z-axis would be pointing up.}
\end{figure}
As the objects moved towards and away from the camera, parts of the objects that should have been hidden were visible, and vice versa. For example, the spaceship engines jut out from the back of the ship. Thus, a viewer positioned in between the two engines should be able to see the right curve of the left engine and the left curve of the right engine, as shown in Figure 7. However, the viewer instead could see the left curve of the left engine and the right curve of the right engine, as seen below right; this perspective made the engines appear recessed instead of external. In order to solve this issue, the z-coordinate of each vertex was multiplied by -1. In conjunction with this fix, the x-value of each obstacle's normal vector was multiplied by -1. This change produced better lighting effects on the obstacles with the new vertex values. The normal vector for the spaceship was left as is.
\begin{figure}[h]
  \includegraphics[width=8cm]{GoodPersp}
  \includegraphics[width=8cm]{BadPersp}
  \centering
  \caption{Two different views of the spaceship model. The left model is the intended view, the right model is how the object was initially rendered in OpenGL.}
\end{figure}

Another struct, \texttt{GameObject}s, is used to hold two three-element arrays; these three variables determine the rotation and position of each obstacle onscreen. A vector of these \texttt{GameObject}s is created in the \texttt{init} function and populated with 7 asteroids. In a for loop, each obstacle in the vector is drawn with its corresponding rotation and position. For the \texttt{glTranslate} calls, the following equation is used to center the asteroids in the xy-plane of the game screen: \texttt{30*obstacles[i].position[0]-15} for x and \texttt{30*obstacles[i].position[1]-15}for y. The bounds on the spaceship are between -10 and 10 on both the x- and y-axis, and this formula bounds the position of the asteroid between -15 and 15. The z-position of the asteroid is determined by \texttt{-90*obstacles[i].position[2]-zpos}.  \\

The \texttt{glRotate} calls use the random values with the equation \texttt{2*obstacles[i].rotation[0]-1} for x, \texttt{2*obstacles[i].rotation[1]-1}, for y, and \texttt{2*obstacles[i].rotation[2]-1} for the z-value of the rotation vector. The angle of rotation is calculated by \texttt{-1.5*zpos}, causing the asteroid to continually rotate as it moves through the scene. By multiplying by 2 and subtracting 1, each component of the rotation vector is bounded between -1 and 1.
\section{Conclusion}
As a whole, the field of constructive solid geometry poses a number of difficult problems for computer scientists. With real-time rendering infeasible, and the alternative algorithms only suitable in a handful of cases, there is still much research to be done. However, the existing solutions are more than adequate to produce usable and complete software, as evidenced by the display program and the asteroid game.
\newpage
\end{doublespace}
\begin{onehalfspace}
\section{Source Code}
\subsection{OpenSCAD}
\subsubsection{die.scad}
% \lstinputlisting[language=scad]{die.scad}
\subsubsection{connector.scad}
%\lstinputlisting[language=scad]{connector.scad}
\subsubsection{torus.scad}
\lstinputlisting[language=scad]{torus.scad}
\subsubsection{asteroid.scad}
\lstinputlisting[language=scad]{asteroid.scad}
\subsubsection{pipes.scad}
\lstinputlisting[language=scad]{pipes.scad}
\subsubsection{spaceship.scad}
\lstinputlisting[language=scad]{spaceship.scad}
\subsubsection{cookie\_cutter.scad}
\lstinputlisting[language=scad]{cookie_cutter.scad}

>>>>

The increased movement of the game objects highlighted one major challenge of converting the OpenSCAD designs to OpenGL. OpenSCAD uses a right-handed coordinate system, while OpenGL uses a left-handed system.
\begin{figure}[h]
  \includegraphics[width=12cm]{Right-Hand}
  \centering
  \caption{The OpenSCAD viewer. As indicated by the legend in the bottom-left corner, the program uses a right-handed coordinate system (the positive z-axis is pointing up). In a left-handed coordinate system, such as the one used by OpenGL, the negative z-axis would be pointing up.}
\end{figure}
As the objects moved towards and away from the camera, parts of the objects that should have been hidden were visible, and vice versa. For example, the spaceship engines jut out from the back of the ship. Thus, a viewer positioned in between the two engines should be able to see the right curve of the left engine and the left curve of the right engine, as shown in Figure 7. However, the viewer instead could see the left curve of the left engine and the right curve of the right engine, as seen below right; this perspective made the engines appear recessed instead of external. In order to solve this issue, the z-coordinate of each vertex was multiplied by -1. In conjunction with this fix, the x- and y-values of each obstacle's normal vector was multiplied by -1. This change produced better lighting effects on the obstacles with the new vertex values. The normal vector for the spaceship was left as is.
\begin{figure}[h]
  \includegraphics[width=8cm]{GoodPersp}
  \includegraphics[width=8cm]{BadPersp}
  \centering
  \caption{Two different views of the spaceship model. The left model is the intended view, the right model is how the object was initially rendered in OpenGL.}
\end{figure}

Another struct, \texttt{GameObject}s, is used to hold two three-element arrays; these three variables determine the rotation and position of each obstacle onscreen. A vector of these \texttt{GameObject}s is created in the \texttt{init} function and populated with 7 asteroids. In a for loop, each obstacle in the vector is drawn with its corresponding rotation and position. For the \texttt{glTranslate} calls, the following equation is used to center the asteroids in the xy-plane of the game screen: \texttt{30*obstacles[i].position[0]-15} for x and \texttt{30*obstacles[i].position[1]-15}for y. The bounds on the spaceship are between -10 and 10 on both the x- and y-axis, and this formula bounds the position of the asteroid between -15 and 15. The z-position of the asteroid is determined by \texttt{-90*obstacles[i].position[2]-zpos}.\\

The \texttt{glRotate} calls use the random values with the equation \texttt{2*obstacles[i].rotation[0]-1} for x, \texttt{2*obstacles[i].rotation[1]-1}, for y, and \texttt{2*obstacles[i].rotation[2]-1} for the z-value of the rotation vector. The angle of rotation is calculated by \texttt{-1.5*zpos}, causing the asteroid to continually rotate as it moves through the scene. By multiplying by 2 and subtracting 1, each component of the rotation vector is bounded between -1 and 1.
\section{Conclusion}
As a whole, the field of constructive solid geometry poses a number of difficult problems for computer scientists. With real-time rendering infeasible, and the alternative algorithms only suitable in a handful of cases, there is still much research to be done. Although this OpenGL implementation was not ideal for rendering the more complicated CSG shapes, such as the torus, this solution was more than adequate to produce usable and complete software. Future work can be done to increase the speed of the software for these complex shapes, as well as combining CSG and collision detection to improve the asteroid game.
\newpage
\end{doublespace}
\begin{onehalfspace}
\section{Source Code}
\subsection{OpenSCAD}
\subsubsection{die.scad}
\lstinputlisting[language=scad]{die.scad}
\subsubsection{connector.scad}
\lstinputlisting[language=scad]{connector.scad}
\subsubsection{torus.scad}
\lstinputlisting[language=scad]{torus.scad}
\subsubsection{asteroid.scad}
\lstinputlisting[language=scad]{asteroid.scad}
\subsubsection{pipes.scad}
\lstinputlisting[language=scad]{pipes.scad}
\subsubsection{spaceship.scad}
\lstinputlisting[language=scad]{spaceship.scad}
\subsubsection{cookie\_cutter.scad}
\lstinputlisting[language=scad]{cookie_cutter.scad}
